---
title: 'Class 11: Scraping Multiple Webpages'
author: "Amelia Hopkins"
date: "2026-09-30"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives

- Enable you to scrape multiple webpages (from the same site), using a `for` loop type approach.

- Enable you to scrape multiple webpages (from the same site), using the [purrr package](https://purrr.tidyverse.org/), which is a functional programming approach.
*Note:* In this process, we will create our own function.

## Re-examining the bulletin example

Let us try to expand on the example from last class using the following:
[ACC](https://bulletin.miamioh.edu/courses-instruction/acc/),
[BUS](https://bulletin.miamioh.edu/courses-instruction/bus),
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa), and
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt).

**COMMENT:** Obviously, you can repeat your code few times with changing the URL. This will work for a few links but would be quite tedious for large amounts of scraping. We will follow the **DRY PRINCIPLE:**, which stands for **Don't Repeat Yourself**.

```{r bulletin}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')


courses_df = data.frame() # Initializing a container to store stuff in from the loop
for(abbrv in dept_abbrv) {
  cat( rep("-", 50), "\n") # cat concatenates, rep
  print(abbrv)
  bulletin_url = paste0(
    'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/'
  )
  # paste0() glues together different pieces of text with nothing separating them
  
  # Q: Why did Fadel make this an R object instead of a string like last class?
  # We did this so we can reuse the rest of our code with only changing the URL
  
  webpage = rvest::read_html(bulletin_url)
  
  
  webpage |> rvest::html_elements("strong") |>
    # Gets all the info that is in strong on the webpage
    rvest::html_text2() -> titles
  # html_text2() cleans up the data. You are retrieving the text from elements and making it more readable
  webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc= descs)
  # Left side is the column name, right side is the object in R that I am assigning the column name
  print(df$title[1:2])
  courses_df = rbind(courses_df, df)
}
```


## `purrr` approach for the same problem

This is a functional programming approach, and we will write our own function. In R, we use the function called `function` to create a function. As opposed to Python, R functions return a single object.

```{r purrr}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')

# This function takes an abbrv as an input and returns a data_frame as an output
scrape_mu_bulletin = function(abbrv){
  bulletin_url = paste0(
    'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/'
  )

  webpage = rvest::read_html(bulletin_url)
  
  
  webpage |> rvest::html_elements("p.courseblocktitle") |> rvest::html_text2() -> titles
  webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  return(df)
}

test = scrape_mu_bulletin(abbrv = 'esp')

# To use functions from purrr, we will use a map_*(), or a map2_*(), or a pmap_*()
# map uses a function that takes a single input (or you are only changing a single input)
# map2 uses a function that takes two inputs
# pmap takes greater than three inputs
# after the _, you put the type of object you are getting back

# The .x is the vector that we will iterate over
# The .f is the function we use
courses_df_from_purrr = purrr::map_df(.x = dept_abbrv, .f = scrape_mu_bulletin)
```

## Scrape Data from the website planecrashinfo

The website that we want to scrape is called: <https://www.planecrashinfo.com/> and it contains a database of plane crashes by year.

```{r}
year = 2025

crash_url = paste0('https://www.planecrashinfo.com/', year, '/', year, '.htm')

crash_page <- rvest::read_html(crash_url, encoding = "ISO-8859-1")

# This should now print without the error
crash_page

## {html_document}
## <html>
## [1] <head>\n<meta http-equiv="Content-Type" content="text/html; charset=UTF-8 ...
## [2] <body>\n<p align="center"><b><font face="Arial" color="#B0B6FF" size="5"> ...

# How many <table> elements are on the page?
crash_tables <- crash_page |>
  rvest::html_elements("table") |>
  rvest::html_table()
```

