---
title: "Class 10: Web Scraping"
author: "Amelia Hopkins"
date: "2026-09-28"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 'robotstxt' example: MU bulletin

In the chunk below, we used the [robotstxt package](https://github.com/ropensci/robotstxt) to check if we are allowed to write a program that scrapes the page

```{r bulletin}
robotstxt::paths_allowed(paths = "courses-instruction/isa/", domain = "https://bulletin.miamioh.edu")
```

## Check Three Sites

TRUE means we are allowed to scrape it
bot = "*" checks to see if a bot is allowed to use the page

```{r}
robotstxt::paths_allowed(paths = "/wiki/Miami_Redhawks_football", domain = "en.wikipedia.org", bot = "*")

robotstxt::paths_allowed(paths = "/jobs/", domain = "www.linkedin.com", bot = "*") # In the robotstxt file for LinkedIn, it indicates that any undefined user (*) is not allowed to crawl the site

robotstxt::paths_allowed(paths = c("/jobs","/viewjob"), domain = "www.indeed.com", bot = "*") # Can scrape the domain but not the path. When R is processing your code, it evaluates the domain before the path, even though when you type the code you type the path first
```

## rvest process

Read it, Select it, Extract it
You need 1 rvest function per step

## Demo: Scraping Miami's Bulletin for ISA

```{r scrape}
# Checking whether we are allowed to scrape this info
# This was done above and found to be TRUE

# I will load the back-end of the html into R using:
# [a] the rvest::read_html() | sometimes rvest::read_html_live() if the page has some dynamic content
# [b] in some cases, we will craft this as a request as shown in slides httr2::request() > .... > httr2::resp_body_html()
isa_courses_in_r = rvest::read_html("https://bulletin.miamioh.edu/courses-instruction/isa/")

# We will extract the course titles, which we can do in a single pipeline
# given that they look the same on the rendered webpage in Chrome
# (bolded, same font size and same font type)

# CSS selector was obtained by: 
# [a] highlighting what we wanted to pull (ISA 401 course title) -> right click
# inspect -> right click > copy -> copy selector
# [b] from this specific example, we were able to get just the title for ISA 401
# because we had the `:nth-child(24)` -> if you were to drop it --> you get all the course titles
isa_courses_in_r |>
  rvest::html_elements("#sc_sccoursedescs > div:nth-child(24) > p.courseblocktitle > strong") |>
  rvest::html_text2() -> isa_titles

isa_courses_in_r |>
  rvest::html_elements(".courseblockdesc") |>
  rvest::html_text2() -> isa_desc

df = data.frame(title = isa_titles, description = isa_desc)
```



